Logsums

### 2019-09-17 03_logsums.Rmd
Update logsums page

```{r setup}
knitr::opts_chunk$set(cache = TRUE)
library(tidyverse)
library(sf)
library(spdep)
library(leaflet)
library(lubridate)
```

@@

We use this function with asserted beta values of -1.98 and 0.3 to calculate the
accessibility logsum.
```{r logsum_vars}
open_spaces$acres <- as.numeric(open_spaces$acres)
logsum_vars <- tracts %>%
  transmute(
    geoid, 
    # Log-sum based utilities, without and with Twitter data
    access_ls = calculate_park_logsums(
      log(distances) * -1.768, log(open_spaces$acres) * 0.373
    ),
    tweets_ls = calculate_park_logsums(
      log(distances) * -1.768, 
      log(open_spaces$acres) * 0.373 + 
        0.1 * yeo.johnson(open_spaces$tweet_count, lambda = 0)
    ),
    multi_ls = calculate_park_logsums(
      log(distances) * -1.768, 
      log(open_spaces$acres) * 0.373 + 
        open_spaces$trails * 0.99 + 
        open_spaces$playgrounds * 0.26 + 
        open_spaces$courts * 0.43
    ),
  ) %>%
  mutate_at(
    vars(ends_with("_ls")),
    # Normalize the logsum onto the Z-scale
    funs( (. - mean(.) ) / sd(.))
  ) %>%
  st_set_geometry(NULL) %>%
  as_tibble()
```

>>>>

```{r setup}
knitr::opts_chunk$set(cache = TRUE)
library(tidyverse)
library(sf)
library(spdep)
library(leaflet)
library(lubridate)
library(VGAM)
```

@@

We use this function with asserted beta values of -1.98 and 0.3 to calculate the
accessibility logsum.
```{r logsum_vars}
open_spaces$acres <- as.numeric(open_spaces$acres)
logsum_vars <- tracts %>%
  transmute(
    geoid, 
    # Log-sum based utilities, without and with Twitter data
    access_ls = calculate_park_logsums(
      log(distances) * -1.768, log(open_spaces$acres) * 0.373
    ),
    tweets_ls = calculate_park_logsums(
      log(distances) * -1.768, 
      log(open_spaces$acres) * 0.373 + 
        0.1 * yeo.johnson(open_spaces$tweet_count, lambda = 0)
    ),
    multi_ls = calculate_park_logsums(
      log(distances) * -1.768, 
      log(open_spaces$acres) * 0.373 + 
        open_spaces$trails * 0.99 + 
        open_spaces$playgrounds * 0.26 + 
        open_spaces$courts * 0.43
    ),
  ) %>%
  mutate_at(
    vars(ends_with("_ls")),
    # Normalize the logsum onto the Z-scale
    list(~ (. - mean(.) ) / sd(.))
  ) %>%
  st_set_geometry(NULL) %>%
  as_tibble()
```
